---
title: "Automatic Model - Iris"
author: "Chapman Siu"
date: "Thursday, February 05, 2015"
output: html_document
---

This is my attempt at building an automatic classifier. I intend on using this with triage process in fraud since I have not completely seen the model, and waiting for access. With the sample data set of 20 observations, and also with the data dictionary inexplicable down, there was little I could do besides preparing for access and setting up potential models and approaches to automate the triage process:

```{r, echo=FALSE, message=FALSE}
library(magrittr)
library(dplyr)
library(caret)
# if used in another setting it would look like this:

automatic.classify <- function(data, response, outdir=".", ...){
  data_summary = summary(data)
  #' DO STUFF:-output summary results
  
  # sample  
  get_samples <- stratify(data, response)
  
  models <- train_caret(get_samples$train, response)
  #' DO STUFF: output summary of the models and the parameters trained and searched
  #' make sure you output the graphs
  
  confusion <- confusion_matrix(models, data, response, ...)
  #' DO STUFF: plot the confusion matrix
  #' make sure you plot the graphs as needed
  
  return(models)
}

```



```{r, echo=FALSE, message=FALSE}
stratify <- function(data, response, frac=.5, seed=10, ...) {
  set.seed(seed)
  if(class(data[, response])=="factor"){
    by_data <- data %>% group_by_(response)
    train <- sample_frac(by_data, frac)
    test <- data[-as.numeric(rownames(train)),]
  } else {
    train <- sample_frac(data, frac)
    test <- data[-as.numeric(rownames(train)),]
  }
  return(list(train=train, test=test))
}

train_caret <- function(train, response, methods=c("rpart", "nnet", "svmRadial", "gam")) {
  control <- trainControl(method="repeatedcv", number=5, repeats=1,
                          index=createFolds(train[,response]))
  models <- Map(function(method) {
    model <- tryCatch(
          train(as.formula(paste(response, "~ .")), data=train, method=method, trControl=control),
          error=function(e) NULL)
    return(model)
  }, methods)
  
  return(models)
}

confusion_matrix <- function(test, response, models) {
  return(Map(function(model){
    fit_test <- predict(model, newdata=test[,!(names(iris) == response)])
    cm <- confuctionMatrix(fit_test, test[,(names(iris) == response)])
  }, models))
}
```

# Abstract

This is an automatic report for the

```{r}
data(iris)
response <- "Species"
```

```{r, echo=FALSE, message=FALSE}
get_samples <- stratify(iris, response)

# test on full set first...
get_samples <- list(train=iris, test=iris)
```

data set. This approach in automated classification involves heavy use of the `caret` library with cross validation on half of the data to determine the optimal classifier. The optimal model of each class is chosen via `caret::train` which in turn is compared against other models. We shall choose the model with the best performance against our hold-out sample.

# 1 Brief description of the data set

To conï¬rm that I have interpreted the data correctly a short summary of the data set follows. The target of the classification is:

```{r, echo=FALSE}
response
```

The dimensions of the data set are:

```{r, echo=FALSE}
dim(iris)
```

A summary of these variables is given below:

```{r, echo=FALSE}
summary(iris)
```

# Summary of the model construction

I have compared a number of different model classes. The performance in the cross validation scheme is shown below:

```{r, echo=FALSE, message=FALSE, echo=FALSE, results='hide', warning=FALSE}
models <- train_caret(get_samples$train, response)
```
```{r, echo=FALSE, message=FALSE, echo=FALSE}
Map(function(model) {
  tryCatch(plot(model), error = function(e) NULL)
}, models)
```

# 3 Model Description

In this section I have described the model I have constructed to explain the data. A quick summary is below, followed by the plots of the estimated Accuracy and Kappa coefficient for all the models.

```{r}
bwplot(resamples(models))
```

INSERT VARIOUS CONDITIONS FOR SPECIFIC MODELS?

# 4 Model Criticism

In this section I have attempted to falsify the model I presented above to understand what aspects of the data it is not capturing well. 

INSERT SOMETHING GENERIC
